%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Academic CV
% LaTeX Template
% Version 1.0 (17/05/20)
%
% Author: Justin Chun-ting Ho
%
% This template is modified based on Medium Length Professional CV (Original author: Trey Hunner). Improved support on listing publications and teaching positions.
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the .tex file. The resume.cls file provides the resume style used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[utf8]{inputenc}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Justin Chun-ting Ho} % Your name
\address{27 Rue Saint-Guillaume, 75007 Paris, France} % Your address
\address{+33752410204 ~$\cdot$~ justin.chunting.ho@sciencespo.fr} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf PhD in Sociology, University of Edinburgh} \hfill {\em Expected 2021} \\ 
Supervised by Mr Ross Bond and Dr Michael Rosie. \\
Dissertation title: The Rise of Hong Kong Nationalism on the Edge of Empires. \\
Completed modules in research methods, natural language processing, and nationalism studies.

{\bf MSc in Political Theory, London School of Economics and Political Science} \hfill {\em 2013} \\ 
Dissertation researched Chinese nationalism and its conflict with the Hong Kong identity. \\
Completed modules in the politics and ethics of environmental change, multiculturalism and
nationalism, and the contemporary disputes of justice.

{\bf BSocSc in Government and Public Admin., Chinese University of Hong Kong} \hfill {\em 2012} \\ 
Focused on political philosophy and international political theory. \\
Minor in Sociology. \\

\end{rSection}


%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

\begin{rSubsectionPublication}{Peer-Reviewed Articles and Conference Proceedings}
\item \underline{Ho, J.C.} (2020) How Biased is the Sample? Reverse Engineering the Ranking Algorithm of Facebook's Graph API. \textit{Big Data \& Society} 7(1).
\item \underline{Ho, J.C.} (2019) Assessing the Bias of Facebook's Graph API. \textit{ACM Hypertext and Social Media 2019}. 
\item Soldner, F., \underline{Ho, J.C.}, Makhortykh, M., Van der Vegt, I.W.J., Mozes, M. \& Kleinberg, B. (2019) Uphill from here: Sentiment patterns in videos from left- and right-wing YouTube news channels. \textit{NLP+CSS at NAACL 2019}.
\item Brownlie, J., Dunne, N., Fernández, N., \underline{Ho, J.C.} \& Squirrell, T. (Forthcoming) Troubling content: Guiding discussion of death by suicide on social media. \textit{Sociology of Health and Illness}.
\end{rSubsectionPublication}

\begin{rSubsectionPublication}{Book Chapters and Other Publications}
\item Davidson, E., \underline{Ho, J.C.} \& Jamieson, L. (2019) Computational text analysis using R in Big Qual data: lessons from a feasibility study looking at care and intimacy. In: Weller, S. and Edwards, R. and Jamieson, L. \& Davidson, E. (eds). Analysing large volumes of complex qualitative data - Reflections from a group of international experts. \textit{NCRM Working Paper}. Accessible: http://eprints.ncrm.ac.uk/4266/
\item \underline{Ho, J.C.} (2017) Book review: Dynamics of National Identity: Media and Societal Factors of What We Are. \textit{Nations and Nationalism} 23(4), pp. 1004–1006.
\item \underline{Ho, J.C.} (2017) Quebec nationalism: the lesson for Hong Kong. In: Fong, C. (ed). \textit{Hong Kong Reformation Theory II}. Hong Kong: Chapter One Publishing. (In Chinese)
\item \underline{Ho, J.C.} (2016) Book review: Nationalism and Contemporary Sino-Japanese Relations: Nation-state, Frontier, and Knowledge of History. \textit{China Information} 30(3), pp. 391-393.
\item \underline{Ho, J.C.} (2015) Localized liberal values: Past and present of the Hong Kong identity. In: Fong, C. (ed).\textit{Hong Kong Reformation Theory}. Taipei: Azoth Books. (in Chinese)
\item Kwong, K. \& \underline{Ho, J.C.} (2015) On Hong Kong self-governing political community: A response to the liberalist. In: Fong, C. (ed). \textit{Hong Kong Reformation Theory}. Taipei: Azoth Books. (in Chinese)
\item Wong, H., Zhang, Y., \underline{Ho, J.C.} \& Ng, S.L. (2016) Understanding the change in youth’s quality of life in light of the Youth Quality of Life Index. In: Chiu, S.W., Ip, J.C. \& Li, H. (eds). \textit{Restless youth: Observation on Hong Kong’s new generation}. Hong Kong: Chung Hwa Book Co. (in Chinese)
\end{rSubsectionPublication}

\newpage
\begin{rSubsectionPublication}{Under Review and Work in Progress}
\item \underline{Ho, J.C.} (Under Review) The root of Nationalism in Hong Kong: Evidence from the Chinese Language Campaign. Progress: Submitted for Initial Review with \textit{Studies in Ethnicity and Nationalism}.
\item Urman, A., \underline{Ho, J.C.} \& Katz, S. (Under Review) “No Central Stage”: Telegram-based activity during the 2019 protests in Hong Kong. Progress: Submitted for Initial Review with \textit{Social Science Computer Review}.
\end{rSubsectionPublication}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Conferences
%----------------------------------------------------------------------------------------

\begin{rSection}{Conference Presentations}
\begin{rSubsectionConference}
\item \underline{Ho, J.C.} (2021, January) Understanding Hong Kong Nationalism with Topic Network. Accepted for oral presentation at AsianPolmeth VIII \& ASQPS IX. Online.
% \item \underline{Ho, J.C.} (2020, July) Moving Beyond Count-based Approach: Understanding Hong Kong Nationalism with Topic Network. Presented at Political Studies Association Early Career Network Conference. Online.
\item \underline{Ho, J.C.} \&  Or, N.H.K. (2020, April) The Rise and Fall of Internet-based Mobilisation during Hong Kong's Anti-Extradition Bill Protests: Evidence from LIHKG Discussion Forum. Accepted for oral presentation at PSA Annual International Conference 2020. Cancelled due to COVID-19.
\item \underline{Ho, J.C.} (2019, July) A Bootstrapping Approach to Assessing the Bias of Facebook’s Graph API. Presented at International Conference on Computational Social Science (IC2S2). Amsterdam, Netherlands.
\item \underline{Ho, J.C.} (2018, December) Assessing the Bias of the New Facebook API. Poster presented at European Symposium Series on Societal Challenges in Computational Social Science. Cologne, Germany.
\item \underline{Ho, J.C.} (2018, August) Facebooking Nationalism: the Construction of Hong Kong Nationalism on Facebook. Presented at the Symposium on Digital Research into Media and Politics. Hong Kong.
\item \underline{Ho, J.C.} (2018, March) One Kingdom, Two Nations: Social Media Analysis of Scottish National Party and UK Independence Party. Presented at The 28th Conference of the Association for the Study of Ethnicity and Nationalism. London, UK.
% \item \underline{Ho, J.C.} (2017, April) Facebooking Nationalism: the Construction of Hong Kong Nationalism on Facebook. Presented at the New Direction Conference. Edinburgh, United Kingdom.
\item \underline{Ho, J.C.} (2017, March) Hong Kong nationalism: ``New nationalism'' with ``old roots''. Presented at The 27th Conference of the Association for the Study of Ethnicity and Nationalism. London, UK.
\item \underline{Ho, J.C.} (2017, March) ``Like of the same'': Facebook like-network of the 2016 Hong Kong Legislative Council Election. Presented at General Online Research 2017. Berlin, Germany.
\item \underline{Ho, J.C.} (2016, June) Constructing the Hong Kong Nation: Cultural Nationalism and Civic Nationalism. Presented at The Asian Conference on Cultural Studies 2016. Kobe, Japan.
\end{rSubsectionConference}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Software
%----------------------------------------------------------------------------------------

\begin{rSection}{Software}

{\bf LIHKGr}{}
R package for scraping text data from LIHKG (Hong Kong's reddit). \\ Source code and releases available at: https://cran.r-project.org/package=LIHKGr

{\bf songotsti}{}
R package for Cantonese tokenisation. \\ Source code and releases available at: https://github.com/justinchuntingho/songotsti.

\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Appointments}

\begin{rSubsection}{Postdoctoral Fellow}{August 2020 - Present}{Sciences Po}{France}
\item Work on the research project ``What do the people want? Analysing Online Populism in Europe and the US'' funded by a VolkswagenStiftung, in collaboration with the Oxford Internet Institute (Oxford University) and GESIS (Cologne).
\item Conduct quantitative text analysis on online populist communication using web-tracking and social media data
\item Develop new methods of multi-language topic modelling using natural language processing methods.
\end{rSubsection}

%------------------------------------------------
\newpage
\begin{rSubsection}{Training Fellow (p.t.)}{October 2019 - July 2020}{University of Edinburgh}{United Kingdom}
\item Develop training programme for the Centre for Data, Culture \& Society to meet the research needs of academic staffs and PhD students.
\item Lead training workshops on computational social science skills, including introduction to R and Python programming, Text Analysis, Data Visualization, Statistical Analysis, and so on.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Research Assistant (p.t.)}{March 2019 - June 2019}{University of Leicester}{United Kingdom}
\item Provided research support for research project, \textit{Big Data Analysis of Mental Health Discussion on Chinese Microblogging site Weibo}.
\item Conduct Chinese organisation and analyse data with several kinds of Text Analysis techniques.
\item Pre-processed the data with R.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Research Assistant (p.t.)}{July 2018 - July 2018}{University of Winchester}{United Kingdom}
\item Provided research support for research project, \textit{Nostalgia in the Social Media}.
\item Developed software to harvest Twitter data.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Research Assistant (p.t.)}{August 2017 - January 2018}{University of Edinburgh}{United Kingdom}
\item Provided research support for the ESRC funded projects, \textit{Working Across Qualitative Longitudinal Studies: a feasibility study looking at care and intimacy} and \textit{A Shared Space and A Space for Sharing} (funded by EMoTICON programme)
\item Analysed text data with Topic Modelling, Keyword Analysis, and Cluster Analysis.
\end{rSubsection}

\begin{rSubsection}{Research Assistant}{February 2015 - September 2016}{Chinese University of Hong Kong}{Hong Kong}
\item Conducted literature review, designed research plans, coordinated and performed data analysis with various advanced quantitative methods.
\item Used Instrumental Variable to estimate the effect of income on subjective wellbeing for the research project, \textit{Using Wellbeing Data in the Valuation of Non-Market Goods: Exploring its Applicability for Use in Hong Kong and China}.

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Lecturing Experience SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Teaching Experience}

{\bf WORKSHOPS} \hfill 

\begin{rSubsectionTeaching}{Instructor for Data Skills Workforce Development Training (Data Carpentry)}{2020}{Bayes Centre, University of Edinburgh, funded by Scottish Funding Council}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Instructor for Collecting Social Media Data}{2020}{Centre for Data, Culture \& Society, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Instructor for Python for Everyone Learning Group}{2020}{Centre for Data, Culture \& Society, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Instructor for Basic Text Analysis using R}{2020}{Centre for Data, Culture \& Society, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Lead Instructor for Data Carpentry}{2020}{Bayes Centre, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Lead Instructor for Data Carpentry}{2019}{Digital Scholarship, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Lead Instructor for R for Data Visualisation and Statistical Analysis}{2019}{Q-Step Edinburgh, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Lead Instructor for Data Carpentry}{2019}{Software Sustainability Institute, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Lead Instructor for Data Carpentry}{2018}{Software Sustainability Institute, University of Edinburgh}{}
\end{rSubsectionTeaching}

{\bf COURSES (LECTURING)} \hfill 

\begin{rSubsectionTeaching}{Guest Lecturer for Using Pre-existing Data for your Own Research}{2019}{School of Social and Political Science, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Guest Lecturer for Researching Digital Life}{2018}{School of Social and Political Science, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Lecturer/Organiser  for Introduction to Text Analysis and Digital Research}{2017}{Institut für Politische Wissenschaft, Leibniz Universität Hannover}{}
\end{rSubsectionTeaching}

% \end{rSection}


%----------------------------------------------------------------------------------------
%	Tutoring Experience SECTION
%----------------------------------------------------------------------------------------


% \begin{rSection}{Tutoring Experience}
{\bf COURSES (TUTORING)} \hfill 


\begin{rSubsectionTeaching}{Tutor for Core Quantitative Data Analysis 1 and 2 (Postgraduate Course)}{2019}{Q-Step, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Tutor for Sociology 2b: Researching Social Life}{2019}{School of Social and Political Science, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Tutor for Core Quantitative Data Analysis 1 and 2 (Postgraduate Course)}{2018}{Q-Step, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Tutor for Statistical Modelling}{2018}{Q-Step, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Tutor for Sociology 2b: Researching Social Life}{2018}{School of Social and Political Science, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Tutor for Doing Social Research with Statistics}{2018}{Q-Step, University of Edinburgh}{}
\end{rSubsectionTeaching}

\begin{rSubsectionTeaching}{Demonstrator for Data Analysis and Research Methods}{2018}{Lothian Equal Access Programme for Schools, University of Edinburgh}{}
\end{rSubsectionTeaching}



\end{rSection}



\begin{rSection}{Academic Affiliations}

\begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
   \itemsep -0.5em % Compress items in list together for aesthetics
    \item AdvanceHE (previously Higher Education Academy), Associate Fellow
    \item The Carpentries, Instructor
    \item Association for the Study of Ethnicity and Nationalism, Edinburgh Branch (ASENE), Member
    \item Centre for Data, Culture \& Society at University of Edinburgh, PhD Affiliate
    \item Edinburgh Text Analysis Research Group, Founder and Convener
\end{list}

\end{rSection}

\begin{rSection}{Awards}
\begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
   \itemsep -0.5em % Compress items in list together for aesthetics
    \item 2019: Gray Scholarship Award, School of Social and Political Science, University of Edinburgh
    \item 2018: Best Poster Presentation, European Symposium on Societal Challenges in Computational Social Science
    \item 2018: Honourable Mention, Summer School Series on Methods for Computational Social Science
\end{list}
\end{rSection}

\begin{rSection}{Funding}
\begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
   \itemsep -0.5em % Compress items in list together for aesthetics
    \item 2020: Early Career Access Fund, Political Studies Association
    \item 2019: Travel Grant, 5\textsuperscript{th} International Conference on Computational Social Science
    \item 2018: Travel Grant, European Symposium on Societal Challenges in Computational Social Science, GESIS
    \item 2018: Travel Grant, Summer School Series on Methods for Computational Social Science, GESIS
    \item 2018: PhD Research Support Fund, University of Edinburgh
    \item 2017: Travel Grant, International Political Science Association
    \item 2017: Digital Scholarship Training Bursaries, University of Edinburgh
    \item 2017: PhD Research Support Fund, University of Edinburgh
\end{list}
\end{rSection}

\begin{rSection}{Academic Service}
\begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
   \itemsep -0.5em % Compress items in list together for aesthetics
    \item Conferences Organised: Co-organiser of the Annual Conference of the Association for the Study of Ethnicity and Nationalism (2019)
    \item Reviewing: SAGE Publishing, \textit{Scottish Affairs}, International Communication Association Annual Conference
    \item Postgraduate Representative, School of Social and Political Sciences, University of Edinburgh (2017-2018)
\end{list}
\end{rSection}






% \begin{rSection}{Methodology Trainings}

% \begin{rSubsection}{Summer School Series on Methods for Computational Social Science}{August 2018}{}{}
% \item Participated in a week-long summer school, worked on the project about social media during crisis.
% \end{rSubsection}

% \begin{rSubsection}{The Alan Turing Institute: Data Study Group	}{December 2017}{}{}
% \item Participated in a week-long hackathon, working on the project “Can the news help us understand global instability?” commissioned by the Cabinet Office, Government of the United Kingdom.
% \end{rSubsection}

% \begin{rSubsection}{Oslo Summer School in Comparative Social Science Studies 2017:}{August 2017}{\bf Collecting and Analyzing Big Data}{}
% \item Completed 20 hours of training on Collecting and Analyzing Big Data.
% \item Covered topics including using API, web scraping, and machine learning.
% \end{rSubsection}

% \begin{rSubsection}{IPSA-NUS Methods School: Quantitative Text Analysis}{June 2017}{}{}
% \item Completed 40 hours of instruction on Quantitative Text Analysis.
% \item Covered topics including topic modeling, sentiment analysis, text/document classification, wordscore, wordfish, POS tagging, and ensemble analysis.
% \end{rSubsection}

% \begin{rSubsection}{CUHK Research Summit: Digital Methods and Social Development}{August 2016}{}{}
% \item Completed a week-long training programme on digital research methods.
% \item Covered ethics of online research, foundations of digital methods; issues mapping; URL list-building and query design; and social media data extraction with Python, Netvizz and Facepager.
% \end{rSubsection}

% \begin{rSubsection}{IPSA-NUS Methods School: Network Analysis}{July 2016}{}{}
% \item Completed 40 hours of instruction on Network Analysis.
% \item Covered topics including graph theory, quadratic assignment procedure, agent based models, and exponential random graph models.
% \end{rSubsection}

% \begin{rSubsection}{IPSA-NUS Methods School: Modern Regression Analysis}{June 2015}{}{}
% \item Completed 40 hours of instruction on Modern Regression Analysis.
% \item Covered topics including ordinary least squares model, interactive model, time series models and models of limited dependent variables.
% \end{rSubsection}

% \end{rSection}




\end{document}
